---
title: "Chapter x: Assessment of the xxx Stock \\ in the xxx region"
date: "`r format(Sys.time(), '%H:%M %B %d, %Y')`"
output:
  pdf_document:
    toc: true
    highlight: zenburn
    fig_caption: yes
    keep_tex: yes
  html_document:
    df_print: paged
fontsize: 11pt
header-includes:
  - \usepackage{fontspec}
geometry: margin=1in
fontfamily: mathpazo
---
\pagenumbering{gobble}

```{r global_options, include=FALSE}

library(knitr)
opts_chunk$set(fig.width = 6, fig.height = 8, echo = FALSE, warning = FALSE, message = FALSE, cache=FALSE,results="asis")
clean_cache(clean = TRUE)
#include = FALSE prevents code and results from appearing in the finished file. R Markdown still runs the code in the chunk, and the results can be used by other chunks.
#echo = FALSE prevents code, but not the results from appearing in the finished file. This is a useful way to embed figures.
#message = FALSE prevents messages that are generated by code from appearing in the finished file.
#warning = FALSE prevents warnings that are generated by code from appearing in the finished.
#fig.cap = "..." adds a caption to graphical results.
#To set global options that apply to every chunk in your file, call knitr::opts_chunk$set in a code chunk. Knitr will treat each option that you pass to 
```
----

\begin{centering}
  Jane Doe, John Doe 
\fontfamily{cmr}
\fontsize{10}{12}
\selectfont
  Alaska Fisheries Science Center, National Marine Fisheries Service \\
  National Oceanic and Atmospheric Administration \\ 
  7600 Sand Point Way NE., Seattle, WA 98115-6349 \\
`r format(Sys.time(), '%B %d, %Y')` \\
\end{centering}
----

```{r giddy}
# settings for speed/updating 
doplots <- F
domcmc  <- F
doproj  <- F
#source("giddyup.R")
```


#  Executive summary

This chapter covers the ...

### Summary of changes in assessment inputs

Relative to last year’s SAFE report, the
following substantive changes have been made in the xxxxxxxxxxx stock
assessment.

#### Changes in the data

   1.	

   2.  
   
### Changes in the assessment methods

There were no changes to the assessment model. An example application of  a
spatial temporal model for  creating an alternative index 


## Summary of xxx results
`r `
\begin{table}[ht]
\centering
\begin{tabular}{lrr|rr}
  \hline
       & \multicolumn{2}{c|}{As estimated or $\mathit{specified}$ } & \multicolumn{2}{c}{As estimated or $\mathit{recommended}$ }  \\
       & \multicolumn{2}{c|}{$\mathit{last}$ year for:}  & \multicolumn{2}{c}{$\mathit{this}$ year for: }               \\
        Quantity & `r thisyr`      &`r thisyr+1`   & `r thisyr+1`      &`r thisyr+2` \\ 
  \hline
	M (natural mortality rate, ages 3+)	&	0.3	&	0.3	&	0.3	&	0.3 \\
Tier	&	1a	&	1a	&	1a	&	1a \\
Projected total (age 3+) biomass (t)	&10,965,000 t & 10,117,000 t &	`r M$age3plus1s` t	   &	`r M$age3plus2s` t  \\
Projected female spawning biomass (t) &	3,678,000 t	&	3,365,000 t	&		`r M$ssb1s` t	         &	`r M$ssb2s` t	      \\
$B_0$                                 &	5,394,000 t	&	5,394,000 t	&		`r M$b0s`,000 t	       &	`r M$b0s`,000 t	    \\
$B_{msy}$                             &	2,042,000 t	&	2,042,000 t	&		`r M$bmsys`,000 t	     &	`r M$bmsys`,000 t	  \\
$F_{OFL}$                             &	0.621	      &	0.621	      &		`r round(M$arithmeanF,3)`	   &	`r round(M$arithmeanF,3)`	\\
$maxF_{ABC}$                          & 0.466	      &	0.466	      &	  `r round(M$harmeanF,3)`	     &	`r round(M$harmeanF,3)`  	\\
$F_{ABC}$                             &	0.336       &	0.336       &		`r (M$fabc1s)`           &	`r (M$fabc2s)`        \\
$OFL$    	                            &	4,797,000 t	&	4,592,000 t	&	  `r M$ofl1s` t          &	`r M$ofl2s` t       \\
$maxABC$    	                        &	3,603,000 t	&	3,448,000 t	&		`r M$maxabc1s ` t      &	`r M$maxabc2s ` t   \\
$ABC$ 	                             &	2,592,000 t	&	2,467,000 t	&		`r M$abc1s ` t         &	`r M$abc2s` t       \\
\hline
Status	                              &	2016	      &	2017	      &		`r lastyr`             &	`r thisyr`          \\
\hline
Overfishing	                          &	No	        &	n/a	      &	No	                       &	n/a                 \\
Overfished	                          &	n/a	        &	No	      &	n/a	                       &	No                  \\
Approaching overfished	              &	n/a	        &	No	      &	n/a	                       &	No                  \\
\hline
\end{tabular}
\end{table}

## Response to SSC and Plan Team comments

### General comments 

In the November 2017 Plan Team minutes: \"The Team recommends that


### Comments specific to this assessment
SSC and Plan Team 2017 minutes:


```{r child = 'maintext.Rmd'}
```
 