---
title: "Chapter x: Assessment of the xxx Stock \\ in the xxx region"
date: "`r format(Sys.time(), '%H:%M %B %d, %Y')`"
output:
  pdf_document:
    toc: true
    highlight: zenburn
    fig_caption: yes
    keep_tex: yes
  html_document:
    df_print: paged
fontsize: 11pt
header-includes:
  - \usepackage{fontspec}
geometry: margin=1in
fontfamily: mathpazo
---
\pagenumbering{gobble}

```{r global_options, include=FALSE}

library(knitr)
opts_chunk$set(fig.width = 6, fig.height = 8, echo = FALSE, warning = FALSE, message = FALSE, cache=FALSE,results="asis")
clean_cache(clean = TRUE)
thisyr  <- 2018
lastyr  <- 2017
#include = FALSE prevents code and results from appearing in the finished file. R Markdown still runs the code in the chunk, and the results can be used by other chunks.
#echo = FALSE prevents code, but not the results from appearing in the finished file. This is a useful way to embed figures.
#message = FALSE prevents messages that are generated by code from appearing in the finished file.
#warning = FALSE prevents warnings that are generated by code from appearing in the finished.
#fig.cap = "..." adds a caption to graphical results.
#To set global options that apply to every chunk in your file, call knitr::opts_chunk$set in a code chunk. Knitr will treat each option that you pass to 
  t1.df         <- as.data.frame(read.table("data/t1.dat",header=TRUE))
  t1.df$Biom    <- format(t1.df$Biom,  big.mark=",",scientific=F,digits=0)
  t1.df$Fofl    <- format(t1.df$Fofl,  big.mark=",",scientific=F,digits=3)
  t1.df$Fmaxabc <- format(t1.df$Fmaxabc,  big.mark=",",scientific=F,digits=3)
  t1.df$Fabc    <- format(t1.df$Fabc,  big.mark=",",scientific=F,digits=3)
  t1.df$SSB     <- format(t1.df$SSB,  big.mark=",",scientific=F,digits=0)
  t1.df$Bmsy    <- format(t1.df$Bmsy,  big.mark=",",kcientific=F,digits=0)
  t1.df$OFL     <- format(t1.df$OFL,  big.mark=",",scientific=F,digits=0)
  t1.df$ABCmax  <- format(t1.df$ABCmax,  big.mark=",",scientific=F,digits=0)
  t1.df$ABC     <- format(t1.df$ABC,  big.mark=",",scientific=F,digits=0)
  t1.df$B0      <- format(t1.df$B0,  big.mark=",",scientific=F,digits=0)
  # Need to replace last two rows w/ current model's result...options are to treat t1.dat as last year's
  # and do the following
  # first move bottom two rows to top two (assuming last year's safe report had the same as recommended)
  #if (update_last_years_values){
    t1.df[1:2,] <- t1.df[3:4,]
    #  t1.df[3:4,] <- Some user function to complete rows given selected model...
  #}
  #else{
   # Table is good as read in (at least for first two rows)
   #  option to do next year's section here...
    #  t1.df[3:4,] <- Some user function to complete rows given selected model...
  #}
```
----

\begin{centering}
  Jane Doe, John Doe 
\fontfamily{cmr}
\fontsize{10}{12}
\selectfont
  Alaska Fisheries Science Center, National Marine Fisheries Service \\
  National Oceanic and Atmospheric Administration \\ 
  7600 Sand Point Way NE., Seattle, WA 98115-6349 \\
`r format(Sys.time(), '%B %d, %Y')` \\
\end{centering}
----

```{r giddy}
# settings for speed/updating 
doplots <- F
domcmc  <- F
doproj  <- F
#source("giddyup.R")
```


#  Executive summary

This chapter covers the ...

### Summary of changes in assessment inputs

Relative to last year’s SAFE report, the
following substantive changes have been made in the xxxxxxxxxxx stock
assessment.

#### Changes in the data

   1. 

   2.  
   
### Changes in the assessment methods

There were no changes to the assessment model. An example application of  a
spatial temporal model for  creating an alternative index 


## Summary of xxx results


\begin{table}[ht]
\centering
\begin{tabular}{lrr|rr}
  \hline
       & \multicolumn{2}{c|}{As estimated or $\mathit{specified}$ } & \multicolumn{2}{c}{As estimated or $\mathit{recommended}$ }  \\
       & \multicolumn{2}{c|}{$\mathit{last}$ year for:}  & \multicolumn{2}{c}{$\mathit{this}$ year for: }               \\
        Quantity & `r thisyr`      &`r thisyr+1`   & `r thisyr+1`      &`r thisyr+2` \\ 
  \hline
 M (natural mortality rate, ages 3+) & 0.3 & 0.3 & 0.3 & 0.3 \\
Tier & 1a & 1a & 1a & 1a \\
Projected total (age 3+) biomass (t)  &  `r t1.df[1,1]` t &  `r t1.df[2,1]` t &  `r t1.df[3,1]` t & `r t1.df[4,1]` t \\
Projected female spawning biomass (t) &  `r t1.df[1,2]` t &  `r t1.df[2,2]` t &  `r t1.df[3,2]` t & `r t1.df[4,2]` t \\
$B_0$                                 &  `r t1.df[1,3]` t &  `r t1.df[2,3]` t &  `r t1.df[3,3]` t & `r t1.df[4,3]` t \\
$B_{msy}$                             &  `r t1.df[1,4]` t &  `r t1.df[2,4]` t &  `r t1.df[3,4]` t & `r t1.df[4,4]` t \\
$F_{OFL}$                             &  `r t1.df[1,5]`   &  `r t1.df[2,5]`   &  `r t1.df[3,5]`   & `r t1.df[4,5]`   \\
$maxF_{ABC}$                          &  `r t1.df[1,6]`   &  `r t1.df[2,6]`   &  `r t1.df[3,6]`   & `r t1.df[4,6]`   \\
$F_{ABC}$                             &  `r t1.df[1,7]`   &  `r t1.df[2,7]`   &  `r t1.df[3,7]`   & `r t1.df[4,7]`   \\
$OFL$                                 &  `r t1.df[1,8]` t &  `r t1.df[2,8]` t &  `r t1.df[3,8]` t & `r t1.df[4,8]` t \\
$maxABC$                              &  `r t1.df[1,9]` t &  `r t1.df[2,9]` t &  `r t1.df[3,9]` t & `r t1.df[4,9]` t \\
$ABC$                                 &  `r t1.df[1,10]` t &  `r t1.df[2,10]` t & `r t1.df[3,10]` t & `r t1.df[4,10]` t \\
\hline
Status                               & 2016       & 2017       &  `r lastyr`             & `r thisyr`          \\
\hline
Overfishing                           & No         & n/a       & No                        & n/a                 \\
Overfished                           & n/a         & No       & n/a                        & No                  \\
Approaching overfished               & n/a         & No       & n/a                        & No                  \\
\hline
\end{tabular}
\end{table}

## Response to SSC and Plan Team comments

### General comments 

In the November 2017 Plan Team minutes: \"The Team recommends that


### Comments specific to this assessment
SSC and Plan Team 2017 minutes:


```{r child = 'maintext.Rmd'}
```